Final Project Code ALL

### 2022-12-08 Draft_Final_Code.Rmd
Finished Code Through Classification

gam_mod1 <- fit(gam_spec,
    Gross ~ s(Runtime) + s(IMDB_Rating) + Meta_score + s(No_of_Votes) + Genre_1,
    data = imdb_clean 
)

@@

```{r}
spline_rec <- recipe(Gross ~ Runtime + IMDB_Rating + Meta_score + 
                   No_of_Votes + Genre_1, data = imdb_clean) %>%
    step_nzv(all_predictors()) %>% 
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors()) %>%
    step_naomit(Gross) %>%
    step_ns(Runtime, deg_free = 2) %>%
    step_ns(No_of_Votes, deg_free = 6) %>%
    step_ns(IMDB_Rating, deg_free = 2)

@@

```{r}
cv_output_spline2 %>% collect_metrics()

### idk what this is for

```{r}
new_mod <- spline_wf %>%
  fit(data = imdb_clean)

new_mod %>%
  tidy()

new_mod %>% 
  tidy() %>% 
  arrange(desc(abs(statistic)))

new_modcv <- fit_resamples(spline_wf, resamples = data_cv10, metrics = metric_set(mae, rmse, rsq))
```

## GAM with Splines and LASSO

### Build and Tune Model

```{r}
# Lasso Model Spec with tune
gam_lasso_spec_tune <- 
  linear_reg() %>%
  set_args(mixture = 1, penalty = tune()) %>% ## mixture = 1 indicates Lasso
  set_engine(engine = 'glmnet') %>% 
  set_mode('regression')

# Recipe with standardization (!) --> just include all these always
data_rec <- recipe(Gross ~ Runtime + IMDB_Rating + Meta_score + 
                   No_of_Votes + Genre_1, data = imdb_clean) %>%
    step_nzv(all_predictors()) %>% # removes variables with the same value (so duplicates don't mess up model)
    step_novel(all_nominal_predictors()) %>% # important if you have rare categorical variables 
    step_normalize(all_numeric_predictors()) %>%  # super important standardization step for LASSO
    step_dummy(all_nominal_predictors()) %>%  # creates indicator variables for categorical variables
    step_naomit(Gross)

# Workflow (Recipe + Model)
lasso_wf_tune1 <- workflow() %>% 
  add_recipe(data_rec) %>%
  add_model(gam_lasso_spec_tune)

# Tune Model (trying a variety of values of Lambda penalty)
penalty_grid <- grid_regular(
  penalty(range = c(-3, 1)),
  levels = 30)

tune_res1 <- tune_grid( # new function for tuning parameters
  lasso_wf_tune1, # workflow
  resamples = data_cv10, # cv folds
  metrics = metric_set(rmse, mae),
  grid = penalty_grid # penalty grid defined above
)

# Visualize Model Evaluation Metrics from Tuning
autoplot(tune_res1) + theme_classic()
```

### Collect CV Metrics and Select Best Model

# Summarize Model Evaluation Metrics (CV)
collect_metrics(tune_res) %>%
  filter(.metric == 'rmse') %>% # or choose mae
  select(penalty, rmse = mean)

best_penalty1 <- select_best(tune_res1, metric = 'rmse') # choose penalty value based on lowest mae or rmse
```

### Fit Final GAM LASSO Model

final_wf_gam_lasso <- finalize_workflow(lasso_wf_tune1, best_penalty) # incorporates penalty value to workflow

final_fit_gam_lasso <- fit(final_wf_gam_lasso, data = imdb_clean)

tidy(final_fit_gam_lasso)
```

```{r}
# Final ("best") model predictors and coefficients

final_fit_gam_lasso %>% tidy() %>% filter(estimate != 0)
```

```{r}
gam_lasso_output <- fit_resamples( 
  final_wf_gam_lasso, # workflow
  resamples = data_cv10, # cv folds
  metrics = metric_set(mae,rmse,rsq)
)

gam_lasso_output %>% collect_metrics()
```

@@

cv_output_spline2 %>% collect_metrics()

gam_lasso_output %>% collect_metrics()
```

The GAM created using TidyModels performs better than the recipe and LASSO GAMs.

@@

### Obtain OOB Predictions and Evaluation Metrics

@@

# Workflow (Recipe + Model) for Full Log Model
log_wf <- workflow() %>%
    add_recipe(logistic_rec) %>%
    add_model(logistic_spec)

@@

@@

*Ask Bryan about relevel factor... do we need it?*

@@

# Recipes and Workflows

```{r}
full_log_wf <- workflow() %>%
  add_recipe(logistic_rec) %>%
  add_model(logistic_spec)

log_model <- fit(full_log_wf, data = imdb_clean_class)

log_modelcv <- fit_resamples(full_log_wf, resamples = data_cv10_class, metrics = metric_set(accuracy,sens,yardstick::spec))

@@

```{r}
# Soft Predictions on Training Data
final_output <- log_fit %>% predict(new_data = imdb_clean_class, type='prob') %>% bind_cols(imdb_clean_class)

@@

@@

```{r}
# thresholds in terms of reference level
threshold_output <- final_output %>%
    threshold_perf(truth = flop, estimate = .pred_FALSE, thresholds = seq(0,1,by=.01))

# J-index v. threshold for no flop
threshold_output %>%
    filter(.metric == 'j_index') %>%
    ggplot(aes(x = .threshold, y = .estimate)) +
    geom_line() +
    labs(y = 'J-index', x = 'threshold') +
    theme_classic()
```

@@

```{r}
# Distance v. threshold for not_spam

@@

@@

@@

```{r}
predict(log_fit, new_data = data.frame(No_of_Votes = 10000, Runtime = 112, IMDB_Rating = 9.8,
                                        Genre_1 = "Drama"), type = "class"
)
```

*Must manually calculate hard prediction*

>>>>

gam_mod1 <- fit(gam_spec,
    Gross ~ s(Runtime, k = 20) + s(IMDB_Rating) + Meta_score + s(No_of_Votes) + Genre_1,
    data = imdb_clean 
)

@@

```{r}
spline_rec <- recipe(Gross ~ Runtime + IMDB_Rating + Meta_score + 
                   No_of_Votes + Genre_1, data = imdb_clean) %>%
    step_nzv(all_predictors()) %>% 
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors()) %>%
    step_naomit(Gross) %>%
    step_ns(Runtime, deg_free = 19) %>%
    step_ns(No_of_Votes, deg_free = 9) %>%
    step_ns(IMDB_Rating, deg_free = 9)

@@

```{r}
cv_output_spline2 %>% collect_metrics()
```

@@

cv_output_spline2 %>% collect_metrics()
```

The GAM created using TidyModels performs better than the recipe and GAMs. Likely has to do with the degrees of freedom of the splines.

@@

### Obtain OOB Predictions and Evaluation Metrics to Choose mtry Value

@@

# Workflow (Recipe + Model) for Full Log Model
log_wf <- workflow() %>%
    add_recipe(logistic_rec) %>%
    add_model(logistic_spec)
```

### Fit Model

@@

### Adds Variable for Odds Ratio

@@

@@

# Cross Validation and Evaluation Metrics

```{r}
log_modelcv <- fit_resamples(log_wf, resamples = data_cv10_class, metrics = metric_set(accuracy,sens,yardstick::spec))

@@

### Picking Threshold

#### Boxplots

```{r}
final_output <- log_fit %>% predict(new_data = imdb_clean_class, type='prob') %>% bind_cols(imdb_clean_class)

@@

#### ROC Curve

@@

#### J Index vs. Threshold

```{r}
# Thresholds in terms of reference level
threshold_output <- final_output %>%
    threshold_perf(truth = flop, estimate = .pred_FALSE, thresholds = seq(0,1,by=.01))

# J-index v. Threshold for no flop
threshold_output %>%
    filter(.metric == 'j_index') %>%
    ggplot(aes(x = .threshold, y = .estimate)) +
    geom_line() +
    labs(y = 'J-index', x = 'threshold') +
    theme_classic()
```

#### J Index vs. Distance

@@

```{r}
# Distance vs. Threshold

@@

### Obtain Evaluation Metrics

@@

### Predictions

@@

We manually performed the hard predictions.
